---
title: "Accuracy"
author: "Mohamed Nachid"
output: pdf_document
---
_boussiala.nachid@univ-alger3.dz_

#How To Estimate Model Accuracy in R Using The Caret Package

#Estimating Model Accuracy



# load the libraries
```{r, echo=T, warning=FALSE, message=FALSE}
library(caret)
library(klaR)
## load the iris dataset
data(iris)
```


##################################################################
##                          Data Split                          ##
##################################################################


## define an 80%/20% train/test split of the dataset
```{r}
trainIndex <- createDataPartition(iris$Species, p=0.80, list=FALSE)
data_train <- iris[ trainIndex,]
data_test <- iris[-trainIndex,]
```
## train a naive bayes model
```{r}
model_split <- NaiveBayes(Species~., data=data_train)
```
## make predictions
```{r}
x_test <- data_test[,1:4]
y_test <- data_test[,5]
predictions <- predict(model_split, x_test)
```
## summarize results
```{r}
confusionMatrix(predictions$class, y_test)
```


#################################################################
##                          Bootstrap                          ##
#################################################################


## define training control
```{r}
train_control_bt <- trainControl(method="boot", number=100)
```
## train the model
```{r}
model_bt <- train(Species~., data=iris, trControl=train_control_bt, method="nb")
```
## summarize results
```{r}
print(model_bt)
```



#################################################################
##                   k-fold Cross Validation                   ##
#################################################################



## define training control
```{r}
train_control_kfcv <- trainControl(method="cv", number=10)
```
## fix the parameters of the algorithm
##grid <- expand.grid(.fL=c(0), .usekernel=c(FALSE))
## train the model
```{r}
model_kfcv <- train(Species~., data=iris, trControl=train_control_kfcv, method="nb")
```
## summarize results
```{r}
print(model_kfcv)
```


##################################################################
##               Repeated k-fold Cross Validation               ##
##################################################################


## define training control
```{r}
train_control_RKFCV <- trainControl(method="repeatedcv", number=10, repeats=3)
```
## train the model
```{r}
model_RKFCV <- train(Species~., data=iris, trControl=train_control_RKFCV, method="nb")
```
## summarize results
```{r}
print(model_RKFCV)
```


##################################################################
##                Leave One Out Cross Validation                ##
##################################################################


## define training control
```{r}
train_control_LOOCV <- trainControl(method="LOOCV")
```
## train the model
```{r}
model_LOOCV <- train(Species~., data=iris, trControl=train_control_LOOCV, method="nb")
```
## summarize results
```{r}
print(model_LOOCV)
```